---
title: "Analysis of chemotherapy trial for colon cancer output"
author: "Luoyan Yong"
date: "10/05/2021"
output: ioslides_presentation
params:
  age: 10
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r, include = FALSE}
#load packages
library(dplyr)
library(tidyverse)
library(survival)
library(survminer)
```

## Description of data
<div> {.notes}
These are data from one of the *first* successful trials of adjuvant chemotherapy for colon cancer. There are two records per person, one for recurrence and one for death. 
</div>

```{r, message = FALSE}
data(colon)
head(colon)
```

## Do females survive better than males?

```{r}
# compute kaplan-Meier survival estimate
fit <- survfit(Surv(time, status) ~ sex, data = colon)

# Change color, linetype by strata, risk.table color by strata
ggsurvplot(fit,
          pval = TRUE, conf.int = TRUE,
          surv.median.line = "hv", # Specify median survival
          palette = c("#E7B800", "#2E9FDF"))
```

The median survival time for sex=1 (Male group) is 2200 days, while it is 2500 days for sex=2 (Female). 

## Do patients older than a specified age survive less? 
It is also interesting to find out if survival rates of treatment differ between patients with older than `r params$age`

```{r}
agegp = dat %>% filter(age > params$age)
ggsurvplot(survfit(Surv(time, status)~ sex, data = agegp))
```